Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Exponentially Increases Repair Time?

### 2015-02-23 phaseDelay.tex
init commit
Updates from ShareLaTeX
added stuff for lucas

\documentclass{sig-alternate}
\usepackage{multirow}
\usepackage{color}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

@@

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Phase Delay Increases  Repair Time. Not.}
\numberofauthors{3}
\author{
\alignauthor
Tim Menzies, \\Carter Pape\\
       \affaddr{CS, NcState, USA}\\
       tim.menzies@gmail.com,\\carterpape@gmail.com
\alignauthor
William Curtis,\\ Forrest Schull\\
\affaddr{SEI, CMU, USA}
wrn,fjshull@sei.cmu.edu
\alignauthor
Lucas \\Layman\\
       \affaddr{Fraunhofer Center,  USA}\\ 
       llayman@fc-md.umd.edu
}

\maketitle
\begin{abstract}
This paper categorically rejects 
the myth that 
the longer a defect persists in a system, the harder
it is to remove that defect.  
This myth is very widely believed
and that the evidence for this myth dates back to certain
isolated studies dating from the 1970s. Recent evidence from
230 software projects from around the world shows that this
myth is completely false.

More important that our particular results, this paper
raises the methodological question of how a small number
of observations from the 1970s can become dogma for decades.
The obvious next question arising from this study is ``how
many other widely held beliefs in software engineering are
not supported by current data?''.
\end{abstract}

@@

\section{Introduction}

\section{Conclusion}

@@

\bibliographystyle{unsrt}
\bibliography{refs}  
\end{document}

>>>>

\documentclass{sig-alternate}
\usepackage{multirow}
\usepackage{color}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}} 
\newcommand{\lucas}[1]{\textcolor{red}{#1}} 
\newcommand{\bill}[1]{\textcolor{blue}{#1}} 
\newcommand{\carter}[1]{\textcolor{cyan}{#1}} 
%\newenvironment{changed}{\par}{\par}

@@

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Exponentially Increases  Repair Time?}
\numberofauthors{3}
\author{
\alignauthor
Tim Menzies, \\Carter Pape\\
       \affaddr{CS, NcState, USA}\\
       tim.menzies@gmail.com,\\carterpape@gmail.com
\alignauthor
William Curtis,\\ Forrest Schull\\
\affaddr{SEI, CMU, USA}
wrn,fjshull@sei.cmu.edu
\alignauthor
Lucas \\Layman\\
       \affaddr{Fraunhofer Center,  USA}\\ 
       llayman@fc-md.umd.edu
}

\maketitle
\begin{abstract}
Does
repair time increases exponentially
the longer a defect persists in a system?
This  is very widely belief and the core rational  for
 rejecting   traditional linear development methods
 in favor of more cyclic agile approaches.

This paper shows that this belief is maintained
quite strongly in the industrial software engineering
community (but, in the academic community, somewhat less so).
Yet based on a sample of 
\carter{230} software projects from around the world from 
\bill{2005 to 2013}, we argue that this belief is mostly 
incorrect. Specifically: the median fix time for issues
is just a few minutes and this increases by a small linear amount
the longer the issue remains in the system.

What was observed was a small number
of defects that take a remarkably long time to resolve
For these issues, if an issue takes more an hour
to resolve then it will usually require many more hours of work.
These long-tail bugs
are more prevalent the longer a project delays issue removal. 
In order to handle such ``long tail'' issues,
we suggest  augmenting software
development groups with additional ``tiger teams'' that are triggered
when issue resolution time increases beyond a certain number of
minutes.
\end{abstract}

@@

\section{Introduction}
Several recent papers call into questions long-held trusims in the field
of software engineering. Devanbu reports that, in practice, the advantage of types languages
is only very minimal. Nagappan et al. found that XXX, contrary to the advice of Dyketra,
it is not necessarily true that ``goto considered harmful'' XXX. More generally,
several recent  papers comment on ``locality'' effects where effects
thold  generally across XXXX

Perhaps it is time to take a look at the base premises of our field, particularly in light of the large software analytics data sets newly available for reseaercehrs.

XXX tsp. 40MB . 235 prokects

\section{Related Work}

In their text Romabach laws

Kent Beck's original extreme programming text is big on this.

Historical  evidence for this dataes back to some studies in the 1970s. To the best of
our knowledge, not updated since. Regardless, as discussed in the next section, this

\input{lucasRelatedWork}

\section{lucasSurvey}

\input{lucas}

\section{billTSP}

\section{carterCharts}

\input{carter}

\sction{Data}

\begin{figure}[!t]

%\renewcommand{\baselinestretch}{0.8}
\scriptsize
\begin{center}
\begin{tabular}{r|rrr|ll}
  Sample&\multicolumn{3}{c|}{Percentiles}\\ 
size & 25th & 50th & 75th & Phase injected & Phase removed\\\hline
57& 6& 16& 47&  BeforeDevelopment&Code\\
72& 2& 4& 11&  BeforeDevelopment&CodeInspect\\
165& 6& 18& 56&  BeforeDevelopment&Test\\
50& 6& 20& 37&  BeforeDevelopment&IntTest\\
42& 8& 28& 65&  BeforeDevelopment&SysTest\\\hline

66& 2& 6& 15&  Planning&Planning\\
41& 1& 5& 16&  Planning&ReqtsReview\\\hline

23& 0& 1& 3&  Reqts&Reqts\\
245& 6& 13& 23&  Reqts&ReqtsReview\\
289& 7& 16& 30&  Reqts&ReqtsInspect\\
32& 6& 21& 40&  Reqts&Design\\
49& 2& 7& 24&  Reqts&DesignInspect\\\hline

94& 2& 5& 10&  HLD&HLDReview\\
133& 3& 8& 19&  HLD&HLDInspect\\
33& 2& 5& 17&  HLD&Design\\\hline

37& 2& 4& 6&  Design&Design\\
455& 11& 24& 53&  Design&DesignInspect\\
218& 5& 14& 30&  Design&Code\\
166& 4& 11& 22&  Design&CodeInspect\\
542& 14& 31& 60&  Design&Test\\
67& 6& 15& 40&  Design&IntTest\\
92& 10& 25& 53&  Design&SysTest\\\hline

53& 2& 4& 9&  DesignInspect&DesignInspect\\
38& 1& 3& 9&  DesignInspect&Code\\\hline

126& 4& 12& 31&  Code&Code\\
459& 11& 24& 45&  Code&CodeInspect\\
461& 11& 26& 55&  Code&Test\\
348& 10& 26& 62&  Code&IntTest\\
230& 8& 18& 39&  Code&SysTest\\
71& 2& 11& 28&  Code&AcceptTest\\\hline

64& 2& 4& 10&  CodeInspect&CodeInspect\\
57& 2& 5& 13&  CodeInspect&Test\\\hline

110& 3& 10& 23&  Test&Test\\
66& 2& 4& 12&  Test&QualTest\\\hline

32& 1& 2& 4&  IntTest&QualTest\\
36& 1& 11& 30&  IntTest&IntTest\\
21& 1& 2& 5&  IntTest&SysTest\\
 \end{tabular}
\end{center}
\caption{Distribution of fix times seen in SEI TSP data.}
\label{fig:faw}
\end{figure}

\begin{figure}
\begin{center}
\scriptsize
\begin{tabular}{rrl}
year& \# issues&\\\hline
2006 &  44 &\\
2007 &  34 &\\
2008&  288 &\rule{1mm}{2mm}\\
2009&  846 &\rule{3mm}{2mm}\\
2010& 1007 &\rule{3mm}{2mm}\\
2011& 3273 &\rule{10mm}{2mm}\\
2012&18102 &\rule{45mm}{2mm}\\
2013&20336 &\rule{50mm}{2mm}\\
2014& 3307 & \rule{10mm}{2mm}\\\cline{1-2}
Total:&47228
\end{tabular}
\end{center}
\caption{This paper studies 47,228 issues recorded 2006 to 2014.}\label{fig:years}
\end{figure}
\begin{figure*}
\begin{center}
\includegraphic[width=6in]{waterfall.png}
\end{center}
\caption{Some parts of the waterfall cycle.}
\end{figure*}
\begin{figure}
\begin{center}
\includegraphic[width=3.5in]{agile.png}
\end{center}
\caption{Some parts of the waterfall cycle.}
\end{figure}

\begin{figure*}[!t]

\renewcommand{\baselinestretch}{0.7}
\small
\begin{center}
\begin{tabular}{ll|r|rl}
            &                  & Sample\\
Phase injected & Phase removed & size & \multicolumn{2}{l}{Scale up, w.r.t. to first phase}
\input{deltas}
\end{tabular}
\end{center}
\caption{Scale ups for median time to resolve issues (taken from \fig{raw}).}
\label{fig:scale}
\end{figure*}

The starting point for this paper were the times required to fix 47,228 issues.
All data was collected
by the Software Engineering Institute in the period 2006 to 2014 (see \fig{years}).
To the best of our knowledge, this is the largest sample of ``time to fix issues''
yet analyzed.

This data was collected using the   methodology described by
Watts Humphrey's Team Software Process~\cite{tsp00}. TSP is an extension of Humphrey's early
work on Personnel Software Process~\cite{psp05}.  PSP encourages developers to continually make estimates
about their day-to-day tasks, then compare those estimates against the actual development effort
(in this way, developers can acquire a more realistic understanding of their work behaviour).

In all data, was collected from 172 separate projects. Given Beck's comments (above) about phase delay motivating agile processes, we take care to identify the differences of these 
projects to agile development projects. In what we call a ``standard agile'' project, there exists
some backlog of tasks. When teams complete their current tasks, they reach into to the backlog
to select the next task(s) to complete. That selection process may use a variety of criteria
to prioritize which  tasks are selected (for more details on that selection process, see~\cite{me09j,port08,boehmturner03}). Tasks are completed in ``sprints'' that can last hours,
days, but rarely not more than weeks. Each day meet for brief ``scrum'' sessions to assess (and possibly alter) their current progress on the goals of the spring.

One way to characterize the above is a ``micro cyclic'' approach where teams 
constantly reassess their priorities using feedback gained after trying to code 
functionality X,Y,Z. An alternate, more traditional approach is a ``macro linear''
approach such as the ``waterfall methodology'' that develops code after an extensive
pre-planning stage:

\[
\mathit{Reqts}
\mathit{ReqtsReview}
\mathit{ReqtsInspect}

\mathit{HighLevelDesign}
\mathit{HighLevelReview}
\mathit{HighLevelInspect}

\mathit{Design}
\mathit{DesignReview}
\mathit{DesignInspect}

\mathit{Code}

\mathit{Compile}
\mathit{Test}
\mathit{IntTest}
\mathit{SysTest}
\]

In the original paper defining and 
critiquing ``waterfall'', Royce defines a set of assessment and feedback processes
such that

care to contrast these 
The majority of the teams follow a basically linear process within a single feature of physical component (usually no more than a week or two work in total). Unlike some agile teams, *most*TSP teams will not conflate development and unit test.  This is usually pretty clear from the task  phase sequencing. A few teams choose to follow a Test Driven Development like process in which code review or inspection will follow test. In a more traditional “micro-linear” TSP approach, unit test follows inspections.

Our data reporting the time required
to resolve issues in phase $j$ that there were introduced in phase $i, i<j$.

The defect typ that we studied were
\be 
\item design, compile, test, or other support system problems = Environment
procedure calls and reference, I/O, user formats = Interface
structure, content = Data
comments, messages = Documentation
spelling, punctuatio typos, instruction formats = Syntax
logic, pointers, loops, recursion, computation, function defects = Function
error messages, inadequate checks = Checking
change management, library, version control = Build, package
declaration, duplicate names, scope, limits = Assignment
configuration, timing, memory = System
\section{Conclusion}

@@

\bibliographystyle{unsrt}
\bibliography{refs}

\end{document}
